---
title: "Example Report"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---

This report show that the results can exported in an [R Markdown](http://rmarkdown.rstudio.com) Notebook. Execute with Run All or Knit to HTML in RStudio.

Please also remove example_ and rename to report_(yourname). Your own config files are currently ignored in .gitignore.

```{r setup}

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

knitr::opts_chunk$set(
	fig.asp = 0.5,
	fig.width = 10,
	message = FALSE,
	warning = FALSE,
	include = TRUE
)

```


```{r load files, include=FALSE}

# Please set rund and config
config_file <- "config.R"  
id_to_load <- 1604416986386
source(file = "app_scripts/init.R")

# theme for ggplot
theme_set(
  theme_bw(base_size = 13) + 
    theme(
      legend.title=element_blank(),
      legend.spacing.x = unit(0.1, 'cm')
    )
)

# Load dynamic plots and pages  --------------------------------------------------------

# All plots are defined in this script
source(file = "app_plots/data_main.R")

# global vars
filters <- list(
  iterations = c(iteration_min,iteration_max),
  unit_prefix = "M")
# needed for report
assign("global_unit",filters$unit, envir = .GlobalEnv)
```



## Operational Capacity

In this market the capacity of all technologies develops like that


```{r plot 1}

filters$technologies_checked <- all_technologies
get_plot_filtered("operational_capacities_by_technology", filters)

```

```{r plot 2}

filters$segments_checked <- all_segments
filters$all_in_one_plot <- FALSE
filters$flip_tick_segment <- TRUE
get_plot_filtered("segment_volume", filters)

```


And only renewables develop like that on average (top) and in each iteration (bottom)

```{r}

# TODO Make sure that values are correct
filters$technologies_checked <- c("Photovoltaic PGT", "Hydroelectric", "Onshore wind PGT", "Offshore wind PGT") 

get_plot_filtered("operational_capacities_by_technology", filters)
get_plot_filtered("operational_capacities_by_technology", filters,average = FALSE)


```

## Other plots

Other plots are in the vector plots[]. Use these names in get_plot_filtered()

```{r}
names(plots)
```