---
title: "Example Report"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

This report show that the results can exported in an [R Markdown](http://rmarkdown.rstudio.com) Notebook.

Please remove example_ and rename to report_(yourname). Your own config files are currently ignored in .gitignore.


```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE, 
  warning = FALSE,
  fig.width= 10,
  fig.asp=0.5
  #out.width= 10
  )

source(file = "emlab/init.R")

# theme for ggplot
theme_set(
  theme_bw(base_size = 13) + 
    theme(
      legend.title=element_blank(),
      legend.spacing.x = unit(0.1, 'cm')
    )
)

# Load dynamic plots and pages  --------------------------------------------------------

# All plots are defined in this script
source(file = "emlab/main.R")



# global vars
filters <- list(
  iterations = c(iteration_min,iteration_max),
  unit_prefix = "M")
# needed for report
assign("global_unit",filters$unit, envir = .GlobalEnv)
```



## Operational Capacity

In this market the capacity of all technologies develops like that


```{r}

filters$technologies_checked <- all_technologies

get_plot_filtered("operational_capacities_by_tech", filters)

```

And only renewables develop like that on average (top) and in each iteration (bottom)

```{r}

# TODO Make sure that values are correct
filters$technologies_checked <- c("Photovoltaic PGT", "Hydroelectric", "Onshore wind PGT", "Offshore wind PGT") 

get_plot_filtered("operational_capacities_by_tech", filters)
get_plot_filtered("operational_capacities_by_tech", filters,average = FALSE)


```

## Other plots

Other plots are in the vector plots[]. Use these names in get_plot_filtered()

```{r}
names(plots)
```



